animbook: Visualizing changes in performance measures and demographic affiliations using animation

### 2023-10-28 animbook-journal.Rmd
updated the data section

```{r data-diagram, fig.cap="The data can be provided in the raw or categorized form, and will be processed into the format needed for the animation.", fig.width=8, fig.align='center', out.width="100%", layout = "l-page"}
knitr::include_graphics("figures/data-diagram.png")
```

  In the data structure, there are requirements that must be followed for reproducing the animation. The data must have ID and time variables. These form what we call a unique ID. Also, the values variable can be either a numerical or categorical variable. The type of this variable will determine the stage the data set is in. This format ensures that during the data pre-processing, the R function understands what needs to be done with the data.

  Figure \@ref(fig:data-diagram) shows which stages the data is in, given the type of values variable. Start with the raw data structure. The values are presented in the numerical format. It is referred to as 'raw' because, in the New York Times animation, it is expressed in the categorical format. However, in most cases, the data is in numerical values and requires transformation. The second form is categorized data, as mentioned earlier, which involves transforming numerical into categories. 
This transformation may not be necessary if it already exists in the categorized format, as in the case of political data (party affiliation). The last form is animated data, where the frame is assigned to each unique ID.

>>>>

```{r data-diagram, fig.cap="The animation expects data with an ID and a time variable, along with a numerical variable (raw form), which is possibly converted to categorical (categorized). The data can be provided in the raw or categorized form, and will be processed into the format needed for the animation where the categorical variable is treated as a quantile and an animation frame variable is created.", fig.width=8, fig.align='center', out.width="100%", layout = "l-body"}
knitr::include_graphics("figures/data-diagram.png")
```

  In the data structure, there are requirements that must be followed for reproducing the animation. The data must have at least ID and time variables, in addition to the measured variable which would usually be numeric, but may be categorical.  The ID variable indicates the individual which is followed over time, such as the company name. There may also be a grouping variable, such as country where the company is registered. <!--These form what we call a unique ID. Also, the values variable can be either a numerical or categorical variable. The type of this variable will determine the stage the data set is in. This format ensures that during the data pre-processing, the R function understands what needs to be done with the data.-->

  Figure \@ref(fig:data-diagram) illustrates the expected format of the data and variables created to prepare it for the animation. We start with the raw data structure. The values are presented in the numerical format, which we call the 'raw' form. <!--because, in the New York Times animation, it is expressed in the categorical format.--> In most cases, the measured variable will be numerical and require transformation. The second form is categorized data, which involves transforming numerical variable into categories, typically quantiles. 
This transformation may not be necessary if it is already provided in the categorized format. The last form is animated data, where the frame is assigned to each unique ID.
